\chapter{Subject description}
\label{chp:2}

The subject choosing is free to all participants. The goal is to provide a parallel application with a sound scalability. 
What we chose to do is a financial problem. In the real practice a hedging process can only be carried out in discrete time 
points. Then an error could be generated when the model is continuous. We want to lower the trading frequency 
(discretisation of the studied timeline) in hedging while 
retaining the error within an acceptable level. A mathematical lowest upper bound was raised in this work, which's the best 
estimation for the time being. We then use the Monte Carlo Simulation to heuristically find the best suited discretisation of 
the underlying problem. 

\section{Mathematical modeling of the project}
Equation~\ref{onetimesimu} gives the discrete time hedging error for one time simulation. The goal is to simulate M times where M is 
sufficiently large so that the $Prob$ tends to be stable. The $Prob$ is defined as the number of times out of M when error is less than 
an accepted value $\epsilon$. 
\begin{equation}
\label{onetimesimu}
\begin{split}
M_T^N
&=e^{-rT}f(X_T)-(u(0,x)+\int_0^T\frac{\partial u}{\partial x}(\varphi(t), 
X_{\varphi_t}))d\widetilde{X}_t\\
&=\int_0^T\frac{\partial u}{\partial x}(t, X_t)d\widetilde{X}_t-\int_0^T\frac{\partial u}{\partial x}(\varphi(t), X_{\varphi(t)})d\widetilde{X}_t\\
&=(X_T-K)^+-\mathbb{E}[(X_T-K)^+]-\int_0^T\frac{\partial u}{\partial x}(\varphi(t), X_{\varphi(t)})dX_t\\
&=(X_T-K)^+-x_0N(d_1(0))+KN(d_2(0))-\sum_{i=0}^{n-1}N(d_1(t_i))(X_{t_{i+1}}-X_{t_i})\\
&=(X_T-K)^+-\frac{x_0}{\sqrt{2\pi}}\int_{-\infty}^{\frac{\log(\frac{x_0}{K})+\frac{1}{2}\sigma^2T}
{\sigma\sqrt{T}}}e^{-\frac{v^2}{2}}dv+\frac{K}{\sqrt{2\pi}}\int_{-\infty}^{\frac{\log(\frac{x_0}{K})-\frac{1}{2}\sigma^2T}{\sigma\sqrt{T}}}e^{-\frac{v^2}{2}}dv\\
&-\sum_{i=0}^{n-1}\frac{1}{\sqrt{2\pi}}\int_{-\infty}^{\frac{\log(\frac{X_{t_i}}{K})+\frac{1}{2}\sigma^2(T-t_i)}{\sigma\sqrt{T-t_i}}}e^{-\frac{v^2}{2}}dv(X_{t_{i+1}}-X_{t_i})\\
\end{split}
\end{equation}

The $X_{t}$ is the price of the underlying asset for the option, which is assumed to evolve in time according to the stochastic equation
\begin{equation}
  dX(t) = \mu X(t)dt + \sigma X(t)dB(t)
\end{equation}

In this equation, $\mu$ is the drift of the asset, $\sigma$ is the option volatility, and $B(t)$ is a standard Brownian motion.

The solution of this stochastic differential equation can be written as 
\begin{equation}
  X_{t_i}=X_{t_{i-1}}e^{(\mu-\sigma^2/2)\delta t+\sigma\sqrt{\delta t}\chi}
\end{equation}
where $\chi$ is a normally distributed random variable with zero mean and unit standard deviation, and \\$\delta t = t_i - t_{i-1}$.


By our unpublished theory, the upper bound of $N$ (discrete intervals of hedging) is given by Equation~\ref{upperbound}, which's the best estimation (the lowest upper bound) for the time being. 
\begin{equation}
\label{upperbound}
  N_{max} = \log^3{(1-Prob)e^{\frac{1}{4}}\frac{1}{T^{\frac{1}{4}}\sqrt{\frac{\epsilon}{(\log{\frac{X_0}{K}}+0.5\sigma^2T)\sqrt{2\pi}}}}}\cdot(-\frac{8e^3X_0^2\cdot 16 \cdot e^{\sigma^2}}{27\epsilon^2\pi})
\end{equation}

There's one more thing to mention, we've implemented our own gaussian integral function using Simpson's rule. See equations~\ref{simpson} and \ref{gauss}.

\begin{equation}
\label{simpson}
\int_{a}^{b}f(x)dx\approx \frac{h}{3}\left[f(x_0)+2\sum\limits_{j=1}^{n/2-1}f(x_{2j})+4\sum\limits_{j=1}^{n/2}f(x_{2j-1})+f(x_n)\right]
\end{equation}

\begin{equation}
\label{gauss}
f(x)=\int_{-\infty}^{x}e^{-\frac{t^2}{2}}dt=0.5\times \sqrt{2\pi} + \int_{0}^{x}e^{-\frac{t^2}{2}}dt
\end{equation}





